\documentclass[12pt,a4paper,onecolumn,titlepage]{book}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[margin=90pt]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage{float}
\usepackage[british]{babel}
\usepackage[lined,boxed]{algorithm2e}
\usepackage{subcaption}
\usepackage{microtype}
\author{Nico Andrew Glas}
\title{Diage: A Dialogue Generator}
\DeclareGraphicsExtensions{.png, .jpg}
\graphicspath{ {./img/} }
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\diage}{Rouge\xspace}
\newcommand{\game}[1]{\textbf{#1}}
\newcommand{\gameby}[2]{\game{#1} by {\textit{#2}}}
\newcommand{\citationneeded}{[\textit{citation needed}]}
\newcommand{\rogue}{roguelike\xspace}
\newcommand{\his}{his/her\xspace}
\newcommand{\he}{he/she\xspace}
\makeatletter

\makeatother

\makeindex
\begin{document}
\maketitle
\chapter*{Abstract}
Game development is resource heavy and time consuming.
By using \textit{procedural content generation}(PCG), game developers can save time perfecting and polishing the more critical parts of a game.
A recent trend within game development is to use PCG to create worlds, levels, and quests. And as such we miss a more esoteric application for the techniques such as creating music or, indeed, generating narratives.

This document chronicles the development of a roguelike game and explores the potential of a procedurally generated narrative from a development perspective.
I lay out the details of the narrative planner used to control the narrative and examine a modelling language that can be used in prototyping narrative scenarios.

\chapter*{Acknowledgements}
I would first and foremost like to thank Joris Dormans for granting me this position within the research facility to let me work out any crazy idea I had in my head (and adding a few of his own, mind). 
Your work in the gaming field is an inspiration to us all.
Thanks, to Stefan Leijnen, for your excellent guidance and providing me with the needed mental support.
Without you and Joris, I shudder to think how this project would have gone.

My thanks, and most sincere apologies for all those late nights, to Anne-Marieke Zaal, for being the reason I stopped work and went home.

Additional thanks go to Gerjo Meier, for correcting all those stupid grammar errors and for all those silly discussion we have.

And of course, thank you, the reader, for taking your time and reading this document.

\tableofcontents
\include{chapters/Introduction}
\include{chapters/IS}
\include{chapters/PCG}
\include{chapters/NarrativePlanning}
\include{chapters/DML}
\include{chapters/Conclusion}
\include{chapters/reflection}
\bibliographystyle{plain}
\bibliography{diage}
\end{document}